Brother, Can You Spare a Manufacturing Job? How Voters React to Deindustrialization

### 2021-12-10 Final Draft/Final Draft.Rmd
text and cites

We replicate \cite{BW21}, which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.

@@

Following \cite{BW21}, our unit of analysis is the county. This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy. The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016. We obtain this from XXXXXXXXX

@@

In this choice we diverge from \cite{BW21}, which uses **gross** manufacturing job losses. For example, if a county lost $450$ manufacturing jobs from 2012-2015 and also gained $400$ manufacturing jobs over the same period, this would be $450$ **gross** job losses, but only $50$ **net** job losses. The **gross** measure captures several dynamics unrelated to deindustrialization - for example, seasonal unemployment in a food-manufacturing region, or workers moving between jobs. Thus we believe the **net** job losses over a period are the more accurate measure.

@@

We conduct two related tests of our hypothesis. Our first test involves an instrumental-variable approach. A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump (a singular candidate, after all). To mitigate these risks, \cite{BW21} uses a Bartik instrument, which we adapt. This instrument essentially uses the cross-county distribution of manufacturing employment as a source of exogenous variation.

@@

@@

% The appendix command is issued once, prior to all appendices, if any.
\appendix

\section{Mathematical Appendix}

>>>>

We replicate \cite{Baccini21}, which analyzes the effect of gross manufacturing job losses from 2012 to 2015 on the change in Democratic vote share in the 2016 presidential election.

@@

Following \cite{Baccini21}, our unit of analysis is the county. This allows us to capture not only the direct effects of deindustrialization on laid-off manufacturing workers, but also on the local economy. The primary outcome variable is the county's change in Democratic vote share between 2012 and 2016. We obtain this from XXXXXXXXX

@@

In this choice we diverge from \cite{Baccini21}, which uses **gross** manufacturing job losses. For example, if a county lost $450$ manufacturing jobs from 2012-2015 and also gained $400$ manufacturing jobs over the same period, this would be $450$ **gross** job losses, but only $50$ **net** job losses. The **gross** measure captures several dynamics unrelated to deindustrialization - for example, seasonal unemployment in a food-manufacturing region, or workers moving between jobs. Thus we believe the **net** job losses over a period are the more accurate measure.

@@

We conduct two related tests of our hypothesis. Our first test involves an instrumental-variable approach. A regression of change in Democratic vote share on manufacturing job losses risks endogeneity, in case counties with manufacturing job losses were otherwise predisposed to turn towards Trump (a singular candidate, after all). To mitigate these risks, \cite{Baccini21} uses a Bartik instrument, which we adapt (see \cite{Bartik91}). This instrument essentially uses the cross-county distribution of manufacturing employment as a source of exogenous variation.

@@

Using this instrument, we then conduct a two stage regression. First we estimate manufacturing job loss with the Bartik Instrument

@@

### 2021-12-10 Final Draft/Final-Draft.tex
text and cites

\title{Brother, Can You Spare a Manufacturing Job? How Voters React to
Deindustrialization}

% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
% Surname2: affiliation2, address2, email2. Acknowledgements}}

@@

In this choice we diverge from \cite{BW21}, which uses \textbf{gross}
manufacturing job losses. For example, if a county lost \(450\)
manufacturing jobs from 2012-2015 and also gained \(400\) manufacturing
jobs over the same period, this would be \(450\) \textbf{gross} job
losses, but only \(50\) \textbf{net} job losses. The \textbf{gross}
measure captures several dynamics unrelated to deindustrialization - for
example, seasonal unemployment in a food-manufacturing region, or
workers moving between jobs. Thus we believe the \textbf{net} job losses
over a period are the more accurate measure.

@@

We conduct two related tests of our hypothesis. Our first test involves
an instrumental-variable approach. A regression of change in Democratic
vote share on manufacturing job losses risks endogeneity, in case
counties with manufacturing job losses were otherwise predisposed to
turn towards Trump (a singular candidate, after all). To mitigate these
risks, \cite{BW21} uses a Bartik instrument, which we adapt. This
instrument essentially uses the cross-county distribution of
manufacturing employment as a source of exogenous variation.

>>>>

\title{Brother, Can You Spare a Manufacturing Job? How Voters React to
Deindustrialization}
\shortTitle{Brother, Can You Spare a Manufacturing Job?}
% \author{Author1 and Author2\thanks{Surname1: affiliation1, address1, email1.
% Surname2: affiliation2, address2, email2. Acknowledgements}}

@@

In this choice we diverge from \cite{Baccini21}, which uses
\textbf{gross} manufacturing job losses. For example, if a county lost
\(450\) manufacturing jobs from 2012-2015 and also gained \(400\)
manufacturing jobs over the same period, this would be \(450\)
\textbf{gross} job losses, but only \(50\) \textbf{net} job losses. The
\textbf{gross} measure captures several dynamics unrelated to
deindustrialization - for example, seasonal unemployment in a
food-manufacturing region, or workers moving between jobs. Thus we
believe the \textbf{net} job losses over a period are the more accurate
measure.

@@

We conduct two related tests of our hypothesis. Our first test involves
an instrumental-variable approach. A regression of change in Democratic
vote share on manufacturing job losses risks endogeneity, in case
counties with manufacturing job losses were otherwise predisposed to
turn towards Trump (a singular candidate, after all). To mitigate these
risks, \cite{Baccini21} uses a Bartik instrument, which we adapt. This
instrument essentially uses the cross-county distribution of
manufacturing employment as a source of exogenous variation.
